---
title: "Lab 2 Final Analysis"
author: "Elisabeth Balke, Caleb Purcell, Isaac Miller"
date: "9/12/2020"
output: html_document
---

**Question 5**

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

Analysis 1 - Rating by Company

     Answer: We are comparing ratings by company grouped by company name. After selecting companies with 20 or more chocolate bars, we analyzed the distributions of the boxplots. The company Soma has the best overall chocolate bar rating based on mean average, which is valued above 3.5.
```{r}
head(choco$Company)
cp1<- factor(choco$Company)
str(cp1)
cpnames1<- c("Arete", "A. Morin", "Bonnat", "Fresco", "Guittard", "Soma", "Valrhona", "Zotter")
company1 <- factor(cp1, levels= cpnames1)
table(company1)
boxplot(choco$Rating ~ company1,
        main= "Distributions ratings based on Company",
        xlab= "Companies",
        ylab= "Rating",
        col= "#58FA82")
```


Analysis 2 - Rating by country manufacturer

     Answer: We are comparing ratings by bean origin grouped by country name.  The resulting plot shows the average ratings for each country in the dataset, so the plot is a bit hard to read, but we can still draw some conclusions.  The first notable finding is that a majority of countries share the same median rating, which is 3.25.  Any rating 2.0 or lower can be considered an outlier for most countries.
```{r}
plot(factor(choco$Bean_Origin), choco$Rating, main = 'Country Average Ratings', xlab= 'Country', ylab='Rating')
```
